Hierarchical ARIMA

### 2020-08-11 KB_modeling.Rmd
add some notes

summary(dat$playoffs)
```

@@

```{r}
dat %>%
  ggplot() +
  geom_histogram(aes(x = log(googlehits))) +
  facet_wrap(~phase)

@@

dat %>%
  filter(team == "Houston Astros") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = final_preds), color = "cornflowerblue")
```

@@

```{r}
lump_mod <- lm(qn_ghits ~ payroll + (odds + winpct)*phase + is_playoffs:playoffs, data = dat)

@@

dat %>%
  filter(team == "Los Angeles Dodgers") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")
```
This is much better.

```{r}
library(lme4)

lump_mod <- lmer(qn_ghits ~ payroll + odds + winpct + (is_playoffs:playoffs + 1|team), data = dat)

dat <- dat %>%
  modelr::add_predictions(lmer, var = "lump_preds")

dat %>%
  filter(team == "Los Angeles Dodgers") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")
```

>>>>

summary(dat$playoffs)

## playoffs variable
#  Did Not make Playoffs or WC Play-in 
#  Played in WC Play-In
#  Eliminated Round 1
#  Eliminated Round 2
#  Lost WS
#  Won WS
```

@@

```{r}
dat %>%
  ggplot() +
  geom_histogram(aes(x = log(googlehits))) #+
  #facet_wrap(~phase)

@@

dat %>%
  filter(team == "Baltimore Orioles") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = final_preds), color = "cornflowerblue")
```

@@

```{r}
lump_mod <- lm(qn_ghits ~ payroll + (odds + winpct)*phase + is_playoffs:playoffs:team, data = dat)

@@

dat %>%
  filter(team == "Los Angeles Dodgers") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")

dat %>%
  filter(team == "San Diego Padres") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")
```
This is much better.
